INTELLIGENT SYSTEMS

### 2021-04-20 papers/paper_10.tex
finish paper 10

\subsection{MATERIAL AND METHODS}
\subsubsection{Survey Area and Data Collection}
A dataset was created containing all the sightings of dolphins that took place 
in the years between 2013 and 2018, in the Gulf of Taranto. The collection 
contains a total of 93 different labeled Risso dolphins, but sadly only 23 of 
these were selected as each has at least 15 images on each side of the fin. 
Through the use of an $f_R$ mask filter, 70\% of each image consists of the 
dolphin fin alone, excluding external elements such as the sea. This filter 
led to consider a new dataset containing 433 images belonging to the 23 
dolphins. The $D_{NN}$ dataset used to train CNNs contains images that have 
not been pre-processed by the $f_R$ filter. This latest dataset is made up of 
582 images belonging to 28 different dolphins. A validation dataset was also 
created containing 300 images of known and unknown Risso's dolphins.

@@

\subsubsection{Convolutional Neural Network}
A convolutional neural network (CNN) is used. Its architecture is composed 
of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{CNNDol}). The number of 
parameters and images useful for training the network is less than the most 
widespread neural networks in the state of the art, thus reducing the problem 
of overfitting. This architecture forms the previous NNPool network. The 
dataset used is the one previously mentioned DNN.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool Architecture.png}
    \centering
    \caption{CNN Architecture build for each dolphin.}
    \label{fig:CNNDol}
\end{figure}

\subsubsection{NNPool}

>>>>

\subsection{MATERIAL AND METHODS}
\subsubsection{Survey Area and Data Collection}
A dataset was created containing all the sightings of dolphins that took place 
in the years between 2013 and 2018, in the Gulf of Taranto. The collection 
contains a total of 93 different labeled Risso dolphins, but sadly only 23 of 
these were selected as each has at least 15 images on each side of the fin. 
Through the use of an $f_R$ mask filter, 70\% of each image consists of the 
dolphin fin alone, excluding external elements such as the sea. This filter 
led to consider a new dataset $D_R$ containing 433 images belonging to the 23 
dolphins. The $D_{NN}$ dataset used to train CNNs contains images that have 
not been pre-processed by the $f_R$ filter. This latest dataset is made up of 
582 images belonging to 28 different dolphins. A validation dataset was also 
created containing 300 images of known and unknown Risso's dolphins.

@@

\subsubsection{Convolutional Neural Network}
A convolutional neural network (CNN) is used. Its architecture is composed 
of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{fig:CNNDol}). The number of 
parameters and images useful for training the network is less than the most 
widespread neural networks in the state of the art, thus reducing the problem 
of overfitting. This architecture forms the previous NNPool network. The 
dataset used is the one previously mentioned DNN.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.7\linewidth]{images/paper10/NNPool Architecture.png}
    \centering
    \caption{CNN Architecture build for each dolphin.}
    \label{fig:CNNDol}
\end{figure}

\subsubsection{NNPool}
The proposed strategy is called NNPool. This strategy is based on the composition 
of several CNN networks equal to the number of dolphins present in 
the $D_{NN}$ dataset. The output generated by NNPool is a probability vector \emph{P} 
(Fig. \ref{fig:NNPool output}) where, if there is only one probability $p_i\in P > 51\%$ , then the new 
photo given in input will be labeled as known, otherwise it will be labeled as 
unknown.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.4\linewidth]{images/paper10/NNPool output.png}
    \centering
    \caption{Example of NNPool output. $p_i$ is the probabilities of the fin given in input to belong to the dolphin reported to the $CNN_i$.}
    \label{fig:NNPool output}
\end{figure}

\subsubsection{Evaluation Metrics}
The metrics used to evaluate the performance of the proposed model are as follows:
\begin{enumerate}
    \item \emph{Accuracy}: percentage of correct predictions.
    \item \emph{Sensitivity}: percentage of positive labels considered as positive.
    \item \emph{Specificity}: percentage of negative labels considered as negative.
\end{enumerate}
Images labeled as negative will correspond to unknown classes.

\subsection{EXPERIMENTS AND RESULTS}
To compare the results obtained by NNPool you must first create the RUSBoost 
model. This model uses the $D_R$ dataset on which the Cross-Validation 
technique is used to train the model. The quality of each image can affect 
the model. To solve this problem, a method called Perception based Image 
Quality Evaluator (PIQE scores) is used which determines the type of quality 
(Excellent, Good, Fair, Poor, Bad) based on the score obtained on each 
image (Low is better). The results obtained by RUSBoost are those shown 
in figure \ref{fig: RUSBoostPerf}. Unfortunately, the performance of RUSBoost depends on 
the number of images available for training and the quality of each of them. The 
RUSPool model is then created to compare its performance. This time the 
$D_v$ dataset is used. The accuracy, sensitivity and specificity values achieved 
are visible in table \ref{RUSPoolPerf}. At this point, the performance of CNN networks on 
the $D_{NN}$ dataset is also evaluated. To evaluate the performance of a CNN 
network, and therefore of NNpool, the Cross-Validation strategy is used with 
a number of $n_{cv}$ cycles equal to 10 on a dataset divided into 2/3 of training 
set and 1/3 of test set. The results are averaged across all the $n_{cv}$. Figure \ref{fig: CNNNNPool perfromance} 
shows the results obtained by every CNN network of NNPool which demonstrate 
its superiority over RUSBoost. Since there are dolphins made up of 
a different number of images, when the quantity of images exceeds 3.5\% the 
sensitivity increases, otherwise it decreases. The strong point of the CNN 
network is that it achieves good performance both in case there are many 
low quality images and in case there are few high quality images. As for the 
performances achieved by NNPool, these exceed that of RUSPool. Also regarding 
the training and classification time (recognition of a single unknown 
image), NNPool is less time-consuming than RUSPool.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost performance.png}
    \centering
    \caption{Performances of RUSBoost.}
    \label{fig: RUSBoostPerf}
\end{figure}
\begin{table}[htbp]
    \centering
    \begin{adjustbox}{width=0.6\textwidth}
    \begin{tabular}{|cccc|}
        \hline
        & Accuracy & Sensitivity & Specificity\\
        \hline
        RUSPool & 0.78 & 0.58 & 0.81\\
        NNPool & 0.87 & 0.70 & 0.90\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{RUSPool and NNPool performance on the validation data set $D_v$}
    \label{RUSPoolPerf}
\end{table}

\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool performance.png}
    \centering
    \caption{Performances of every CNN network in NNPool.}
    \label{fig: CNNNNPool perfromance}
\end{figure}

\subsection{CONCLUSION}
In conclusion, it can be said that, among all the methods compared, the 
proposed CNN network has better performances and more advantages. One 
of the first is the non-interaction of the user, while following there is the factor 
of the training and classification speed. Unfortunately, like many CNN-based 
methods, the problem of the number of images, and their quality, still remains 
open in fact by providing a low number of images, all with low quality, the 
proposed algorithm will tend to have low performance in terms classification 
of dolphins.
